\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2016-03-07 write_up/cricket.tex
more regular format for author affil.

\begin{document}
\title{\vspace{-.5cm}\normalsize{Fairly Random: The Impact of Winning the Toss on the Probability of Winning\footnote{The paper benefitted from comments by Andrew Gelman, Donald Green, and Daniel Stone. Scripts used to scrape the data, the final data set, and scripts used for analysis can be found at: \href{https://github.com/dwillis/cricket-stats}{https://github.com/dwillis/cricket-stats}. }\vspace{.5cm}}}
\author{\normalsize{Gaurav Sood}\\\href{mailto:gsood07@gmail.com}{\small{gsood07@gmail.com}} \and \normalsize{Derek Willis}\\\href{mailto:dwillis@gmail.com}{\small{dwillis@gmail.com}}}
\date{\vspace{.5cm}\normalsize{\today}}
\maketitle
\doublespacing

>>>>

\begin{document}
\title{\vspace{-.5cm}\normalsize{Fairly Random: The Impact of Winning the Toss on the Probability of Winning\footnote{The paper benefitted from comments by Andrew Gelman, Donald Green, and Daniel Stone. Scripts used to scrape the data, the final data set, and scripts used for analysis can be found at: \href{https://github.com/dwillis/cricket-stats}{https://github.com/dwillis/cricket-stats}. }\vspace{.5cm}}}
\author{\normalsize{Gaurav Sood}\footnote{Gaurav is an independent researcher. He can be reached at: \href{mailto:gsood07@gmail.com}{\small{gsood07@gmail.com}}} \and \normalsize{Derek Willis}\footnote{Derek is a  news applications developer at ProPublica. He can be reached at: \href{mailto:dwillis@gmail.com}{\small{dwillis@gmail.com}}}}
\date{\vspace{.5cm}\normalsize{\today}}
\maketitle
\doublespacing
